Constraining the High Density Nuclear Symmetry Energy with Pions

### 2020-05-14 chapters/ch_data_analysis.tex
Added GG information
quick update before check

@@

\begin{figure}
\includegraphics[scale=.01]{place}
\caption{A summary of all the effects modeled in the TPC MC simulation.}
\label{fig:place}
\end{figure}

>>>>

\subsection{Experimental Pad Response Function}

The correlations we introduced by only clustering along one direction do not play a significant role in the particle identification, but cause deviations from the expected Gatti distribution. Also, analytic PRFs only exist for classical multi-wire TPCs. For these reasons it is useful to experimentally measure the PRF and fit it with an empirical function, typically a Gaussian, to describe its behavior.

As in Fig.~\ref{fig:topview}, we postulate that the PRF is a function of the total charge deposited in a cluster $Q = \sum_i q_i$, and the difference in position of the center of the $i^{th}$ pad, $x_i$, to the mean position $\bar{x} = \sum_i x_i q_i/Q$, defined as $\lambda_i = x_i-\bar{x}$. The PRF is simply defined as the charge fraction of each pad as a function of $\lambda$, as shown in Equation \ref{eq:prf}.

\begin{equation}\label{eq:prf}
PRF(\lambda_i) = \frac{q_i(\lambda_i)}{Q}
\end{equation}

Averaging over many events in the experimental data, the resulting PRF for the S$\pi$RIT TPC is shown in Fig.~\ref{fig:expprf}. Here we see the deviations from the expected analytic Gatti distribution (black curve), whereas fitting with a two parameter Gaussian function (red curve) gives a better description of the  data, Eq.~\ref{eq:gaus}, with the two parameters being the normalization coefficient, $N_0$, width $\sigma$, and with a mean value assumed to be 0.

\begin{equation}\label{eq:gaus}
PRF_{\mathrm{Gaus}}(\lambda) = N_0 e^\frac{-\lambda^2}{2\sigma^2}
\end{equation}

\begin{figure}[ht!]s
\begin{overpic}[width=\linewidth]{fig5.pdf}
\put(61,55){\contour{white}{ PRF${}_{\mathrm{Gaus}}(\lambda)$ eq. \ref{eq:gaus}  }}
\put(61,49){\contour{white}{ PRF${}_{\mathrm{Gatti}}(\lambda)$ eq. \ref{eq:gatti} }}
\end{overpic}
\caption{Experimental pad response function of many events for a crossing angle of $85^{\circ} < \theta \leq 90^{\circ}$.  }
\label{fig:expprf}
\end{figure}

The shape of the PRF depends on the crossing angle of the track \cite{gatti}. Plotted in Fig.~\ref{fig:prfpimData} is the PRF of $\pi^-$ tracks vs. the crossing angle $\theta$. The PRF gets wider starting from $90^{\circ}$  and going to $45^{\circ}$; if we did not switch clustering directions the PRF would become wider until it was a uniform distribution and there was no position resolution. Since we switch the clustering direction from $x$ to the $z$ direction at $45^{\circ}$, the opposite trend is seen where the PRF becomes narrower as the position resolution gets better going from $45^{\circ}$ to $0^{\circ}$.

\begin{figure}[!htb]
     \centering
	 \includegraphics[width=\textwidth]{PRFs_data_wcut.png}
     \caption{PRF response from $\pi^-$ data. }
     \label{fig:prfpimData}
\end{figure}

\begin{figure}[ht!]
\vspace{5mm}
\includegraphics[width=\linewidth]{fig7}
\caption{Parameters $N_{0}$ and $\sigma$ as a function of the crossing angle $\theta$ with the $4^{th}$ order polynomial fits.}
\label{fig:normsigma}
\end{figure}

\begin{comment}
\begin{table}
\centering
 \begin{tabular}{||c c c c c c||} 
 \hline
 Coefficient & $c_0$ & $c_1$ & $c_2$ & $c_3$ & $c_4$ \\ [0.5ex] 
 \hline\hline
 $0 < \theta < 45$ & & & & &  \\ [.25ex]
 \hline
 $N_0$ & .897 & 5.766E-3 & -4.263E-4 & 7.444E-6 & 5.705E-8 \\ 
 \hline
 $\sigma$ & 5.496 & -3.920E-2 & 2.693E-3 & -5.208E-5 & 5.334E-7\\
 \hline
 $45 < \theta < 90$ & & & &  & \\ [.25ex]
 \hline	
 $N_0$ & 1.220 & -6.258E-2 & 1.608E-3 & -1.492E-5  & 4.654E-8 \\
 \hline
 $\sigma$ & 31.368 & -1.109 & 1.779E-2 & -1.336E-4 & 3.940E-7\\
 \hline
\end{tabular}
\caption{Coefficients of the $4_th$ order polynomial fit to the Gaussian parameters $N_0$ and $\sigma$. The polynomial form is given as $c_0 + c_1 x + c_2 x^2 + c_3 x^3 + c_4 x^4$}
\label{tb:coeff}
\end{table}
\end{comment}

Fits were performed to the experimental data with  $5^{\circ}$ width bins from $0^{\circ} < \theta \leq 90^{\circ}$. The two parameters of the Gaussian fits are plotted versus $\theta$ in Fig.~\ref{fig:normsigma}; a $4^{th}$ order polynomial fit between these points allowed for interpolating between $\theta$.

@@
